Evaluating Class Imbalance

### 2019-05-12 Scripts/evaluating_imbalance_ratios.Rmd
editted results script

# Combined

@@

>>>>

# Combined Plots

@@

# Combined Tables

```{r}
cl.per.chr <- character()
res.per.chr <- character()
chr.per.chr <- character()
bins.per.chr <- numeric()
bounds.per.chr <- numeric()
ir.per.chr <- numeric()

chrs <- paste0("chr", c(1:8,10:22))
for(i in c("GM12878","K562")){
  for(j in c("10kb", "25kb","50kb","100kb")){
    for(k in 1:length(chrs)){
      binslist_dat_center <- readRDS(paste0("Z:/TAD_data_analysis/",
                                            i,
                                            "/",
                                            j,
                                            "/training_testing/binslist",
                                            gsub("kb","",j),
                                            "_center.rds"))

      cl.per.chr <- rbind(cl.per.chr, i)
      res.per.chr <- rbind(res.per.chr, j)
      chr.per.chr <- rbind(chr.per.chr, chrs[k])

      bins.per.chr <- rbind(bins.per.chr, length(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]]))

      bounds.per.chr <- rbind(bounds.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2])

      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1])

    }
  }
}

irtab <- cbind.data.frame(cl.per.chr,
                          res.per.chr,
                          chr.per.chr,
                          bins.per.chr,
                          bounds.per.chr,
                          ir.per.chr)
colnames(irtab) <- c("cl","res","chr","bins","bounds","ir")

irtab_summ <- irtab %>%
  group_by(cl, res) %>%
  summarise(AveBins = mean(bins, na.rm = TRUE),
            AveBinsSD = sd(bins, na.rm = TRUE),
            AveBounds = mean(bounds, na.rm = TRUE),
            AveBoundsSD = sd(bounds, na.rm = TRUE),
            AveIR = mean(ir, na.rm = TRUE),
            AveIRSD = sd(ir, na.rm = TRUE))
```
